Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2017-01-13 analysis/phylopic.tex
Update cached files

% latex table generated in R 3.1.2 by xtable 1.7-4 package
% Sat Nov  8 14:57:15 2014
Taxonomic order & Credit & License URL \\ 
  \midrule
Salmoniformes & Servien (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Gadiformes &  & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Perciformes & Ellen Edmonson and Hugh Chrisp (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Pleuronectiformes & Tony Ayling (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Lepidoptera & Curtis (modified by T. Michael Keesey) & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Rodentia & Mattia Menchetti & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Carnivora & Brian Gratwicke (photo) and T. Michael Keesey (vectorization) & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Lagomorpha & Sarah Werning & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Coleoptera & Crystal Maier & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Odonata & Gareth Monger & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Passeriformes & Michael Scroggie & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Anseriformes & Sharon Wegner-Larsen & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Artiodactyla & Jan A. Venter, Herbert H. T. Prins, David A. Balfour and Rob Slotow (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Diptera & Gareth Monger & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Charadriiformes & JJ Harrison (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Hemiptera & T. Michael Keesey & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Falconiformes & Liftarn & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Galliformes & Steven Traver & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
   \bottomrule

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
Taxonomic order & Credit & License URL \\ 
  \midrule
Gadiformes &  & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Salmoniformes & Servien (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Perciformes & Ellen Edmonson and Hugh Chrisp (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Pleuronectiformes & Tony Ayling (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Lepidoptera & Curtis (modified by T. Michael Keesey) & \url{http://creativecommons.org/publicdomain/mark/1.0/} \\ 
  Carnivora & Brian Gratwicke (photo) and T. Michael Keesey (vectorization) & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Coleoptera & Crystal Maier & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Rodentia & Mattia Menchetti & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Odonata & Gareth Monger & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Lagomorpha & Sarah Werning & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Anseriformes & Sharon Wegner-Larsen & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Passeriformes & Michael Scroggie & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Artiodactyla & Jan A. Venter, Herbert H. T. Prins, David A. Balfour and Rob Slotow (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Diptera & Gareth Monger & \url{http://creativecommons.org/licenses/by/3.0/} \\ 
  Charadriiformes & JJ Harrison (vectorized by T. Michael Keesey) & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Hemiptera & T. Michael Keesey & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
  Falconiformes & Liftarn & \url{http://creativecommons.org/licenses/by-sa/3.0/} \\ 
  Galliformes & Steven Traver & \url{http://creativecommons.org/publicdomain/zero/1.0/} \\ 
   \bottomrule
